---
title: "pipeline"
author: "Elizabeth Madin"
date: "14/05/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Allometry Project

> How does plant height scale with weight?

Hypotheses: 
1) No replationship
2) Linear
3) To the second power
4) To the third power

## Load our data

```{r}
seeds <- read.csv("https://raw.githubusercontent.com/jmadin/himbr/master/data/seed_root_herbivores.csv", as.is=TRUE)
head(seeds)
summary(seeds)

class(seeds["Height"])
class(seeds[["Height"]])

```

## A function for standard error

```{r}
standard_error <- function(x) {
  sd(x) / sqrt(length(x))
  return(se)
}
```

## Seed height/weight plotting

```{r}
plot(Weight ~ Height, data=seeds)

```


## Data transformation

```{r}

seeds$Height_log10 <- log10(seeds$Height)
seeds$Weight_log10 <- log10(seeds$Weight)

```

## Data analysis

We will run a linear regression on log transformed variables to look for scaling coefficients

```{r}

plot(Weight_log10 ~ Height_log10, data=seeds, xlab="Height,log10", col="grey")

mod <- lm(Weight_log10 ~ Height_log10, seeds)
summary(mod)
mod$coef
write.csv(mod$coef, "output/model_coefs.csv")

```

## Plotting

```{r}

#abline(mod)
h <- sort(seeds$Height_log10)
pred <- predict(mod, list(Height_log10=h), interval="confidence")

pdf("figs/figure1.pdf")

plot(Weight_log10 ~ Height_log10, data=seeds)
lines(h, pred[,1], col="black", lty=2)

polygon(c(h, rev(h)), c(pred[,2], rev(pred[,3])), col=rgb(0,0,1,0.2), border=NA)

```

## Conclusions

The slope of the relationship between height and weight is `round(mod$coef[2], 2)`.


